Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Intro to Fam section.

We will consider a total language where types denote sets. The goal is to interpret programs as Galois
connections relating approximations of their input to approximations of their output. Since the appropriate
lattice of approximations depends on the value being approximated, the semantics of every type $\tau$ must
have both a ``conventional'' component assigning $\tau$ to a set $X$, and an associated lattice of
approximations $\partial X(x)$ for every point $x \in X$. An expression $e$ of type $Y$ with a single free
variable of type $X$ must be interpreted as a morphism that combining both a function $f: X \to Y$ and a
family of Galois connections $\partial f(x): \partial X(x) \to \partial Y(f(x))$ for every $x \in X$.

>>>>

We will consider a total language where types denote sets. The goal is to interpret programs as Galois
connections relating approximations of their input to approximations of their output. Since the appropriate
lattice of approximations depends on the value being approximated, the semantics of every type $\tau$ must
have both a ``conventional'' component assigning $\tau$ to a set $X$, and an associated lattice of
approximations $\partial X(x)$ for every point $x \in X$. An expression $e$ of type $Y$ with a single free
variable of type $X$ must then be interpreted as a morphism which also has two components: a function $f: X
\to Y$ giving the baseline (unapproximated) behaviour of the program, plus a family of Galois connections
$\partial f(x): \partial X(x) \to \partial Y(f(x))$ for every $x \in X$ which can be used for program slicing.
